---
title: "Monitoring Women, Peace and Security Agenda around the World"
author: "Nandar Min Tun"
institute: "School of International Service"
date: '2023-05-09'
output: pdf_document
subtitle: ""
xaringan::moon_reader:
  lib_dir: libs
  css: ["style.css"]
  nature:
    highlightStyle: github
    highlightLines: true
    countIncrementalSlides: false
    progress: true
    ratio: "16:15"
    separator: ---
    slideNumber: true
    enableChalkboard: true
    Chalkboard:
      theme: moon
---

- The graphs below display the scores for the WPS Index 2021.
- The WPS Index measures women's well-being and empowerment in countries around the world.
- The scores are based on a range of indicators, including legal frameworks, security, and access to healthcare and education.
- Higher scores indicate better performance on these indicators.

- The graphs below display the scores for the WPS Index 2021.
- The WPS Index measures women's well-being and empowerment in countries around the world.
- The scores are based on a range of indicators, including legal frameworks, security, and access to healthcare and education.
- Higher scores indicate better performance on these indicators.
```{r setup, include=FALSE}

# This "setup" chunk specifies global options
# for handling code, plots, etc in your doc

  knitr::opts_chunk$set(
    echo = TRUE, warning = FALSE, message = FALSE,
    fig.width = 6, fig.asp = 0.618, 
    fig.align = 'center'
  )  

  library(tidyverse)
  library(patchwork)
  library(knitr)
  library(kableExtra)
  library(dplyr)
  library(ggplot2)
  library(xaringanExtra)
```
```{r load WPS, include=FALSE}
    load("wpsdatafinal.RData")
```
### Analysis1: WPS Index Score
```{r A1, echo=FALSE, out.width="110%", out.height="90%", dpi=300, fig.cap="Analysis 1"}

ggplot(data = wpsdatafinal, aes(x = "Quintile", y = as.numeric(WPSIndexScore), fill = Quintile)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07", "#6B3E26", "#5D5D5D")) +
  coord_flip() +
  ylab("WPS Index Score") +
  ggtitle("Distribution of WPS Index Scores by Quintile")
```
---

### Analysis 2: Distibution of Quintiles in terms of WPS and Employment

```{r A2, echo=FALSE, out.width="110%", out.height="90%", dpi=300,fig.cap="Analysis 2"}

library(cowplot)
p <- ggplot(wpsdatafinal, aes(x = Employment, y = WPSIndexScore, color = Quintile)) +
     geom_point(size = 3.5) +
     geom_smooth(method = "loess", se = FALSE) +
     xlab("Employment") +
     ylab("WPS Index Score") +
     ggtitle("Employment vs. WPS Index Score") +
     geom_boxplot(na.rm = TRUE) +
     theme(axis.text=element_text(size=2),
           axis.title=element_text(size=16))

p2 <- p + scale_color_manual(name = "Quintile",
                       values = c("red", "blue","yellow","green","pink"),
                       labels = c("Bottom", "Fourth","Third","Second","First"))

# Create plot with faceted layout with reordered facets
p3 <- ggplot(wpsdatafinal, aes(Employment, WPSIndexScore, color = Quintile)) +
  facet_wrap(~ Quintile, scales = "free", nrow = 3) +
  geom_point(alpha = .8, shape = 1, show.legend = FALSE) +
  geom_smooth(method = "lm", se = FALSE) + 
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  theme_bw() +
  labs(title = "Individual Quintile", x = "Employment", y = "WPS Index Score") +
  theme_bw() +
  guides(colour = FALSE) +
  theme(axis.text=element_text(size=2),
        axis.title=element_text(size=16))

p2 + p3

```

